---
title: "Documentation of Analyses"
csl: bib/apa.csl
date: "25 Juli 2016"
output:
  html_document:
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
bibliography: bib/library.bib
---

# Setup
The following contains the documentation of all analysis conducted for the manuscript entitled __title title XX__ and submitted to __PLoS One__ at xxxx-xx-xx.  
We primarily used the free and open source software R [@RCoreTeam2014]. Multilevel confirmatory factor analysis and multilevel structural equation models were estimated with MPlus 7.1 [@Muthen2012] using the R package `MplusAutomation` [@Hallquist2013] as a R leverage.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(MplusAutomation)
library(lavaan)
```

# Datawrangling
Experimental conditions and rotations of the booklets resulted in 12 different rawdata files. The following code junks descripe their import, joining, recoding and reshaping.


## Import 
```{r import, cache = T}
raw_erf_r1 <- read.table("data/erf_r1/daten.csv", sep = ";", header = T)
raw_erf_r2 <- read.table("data/erf_r2/daten.csv", sep = ";", header = T)
raw_erf_r3 <- read.table("data/erf_r3/daten.csv", sep = ";", header = T)
raw_erf_r4 <- read.table("data/erf_r4/daten.csv", sep = ";", header = T)
raw_exp_r1 <- read.table("data/exp_r1/daten.csv", sep = ";", header = T)
raw_exp_r2 <- read.table("data/exp_r2/daten.csv", sep = ";", header = T)
raw_exp_r3 <- read.table("data/exp_r3/daten.csv", sep = ";", header = T)
raw_exp_r4 <- read.table("data/exp_r4/daten.csv", sep = ";", header = T)
raw_wis_r1 <- read.table("data/wis_r1/daten.csv", sep = ";", header = T)
raw_wis_r2 <- read.table("data/wis_r2/daten.csv", sep = ";", header = T)
raw_wis_r3 <- read.table("data/wis_r3/daten.csv", sep = ";", header = T)
raw_wis_r4 <- read.table("data/wis_r4/daten.csv", sep = ";", header = T)
```


##Joining
```{r joining, message=F, warning=F, cache = T}
rawdata <- full_join(raw_erf_r1,
           full_join(raw_erf_r2,
           full_join(raw_erf_r3,
           full_join(raw_erf_r4,
           full_join(raw_exp_r1,
           full_join(raw_exp_r2,
           full_join(raw_exp_r3,
           full_join(raw_exp_r4,
           full_join(raw_wis_r1,
           full_join(raw_wis_r2,
           full_join(raw_wis_r3, raw_wis_r4)))))))))))
```


## Recoding
```{r recoding, cache = T}
#names(rawdata%>%select(ends_with("_ip")))

rawdata <- rawdata%>%
  mutate(source = as.factor(substr(rawdata$Pseudonym, 1,3)),
         te_01_np = tx_02_np_t1,              ## CAEB recoding and renaming: te = texture, vr = variability
         te_02_np = tx_04_np_t1,   
         te_03_np = 8 - tx_05_ip_t1,
         te_04_np = tx_06_np_t1, 
         te_05_np = tx_07_np_t1,     
         te_06_np = tx_08_np_t1,     
         te_07_np = tx_09_np_t1,     
         te_08_np = tx_10_np_t1,         
         te_09_np = 8 - tx_11_ip_t1,
         te_10_np = tx_12_np_t1,  
         
         vr_01_np = va_01_np_t1, 
         vr_02_np = 8 - va_02_ip_t1, 
         vr_03_np = 8 - va_03_ip_t1, 
         vr_04_np = 8 - va_04_ip_t1, 
         vr_05_np = va_05_np_t1, 
         vr_06_np = 8 - tx_13_ip_t1, 
         vr_07_np = 8 - va_06_ip_t1, 
         
         si_03_np = 7 - si_03_ip,                ## Study interest
         si_04_np = 7 - si_04_ip,
         si_06_np = 7 - si_06_ip,
         
         sk_03_np = 5 - sk_03_ip,                ## Self-Concept
         
         
         ## Worked out examples text
         dd_we_ie_05_np = 7 - dd_we_ie_05_ip,    ## Interest-Enjoy
         dd_we_tp_02_np = 5 - dd_we_tp_02_ip,    ## Theory-Praxis-Relation
         dd_we_tp_04_np =     dd_we_tp_04_ip,
         dd_we_tp_06_np =     dd_we_tp_06_ip, 
         dd_we_ko_02_np = 5 - dd_we_ko_02_ip,    ## Koherence
         dd_we_ko_04_np = 5 - dd_we_ko_04_ip, 

         ## CTM text
         dd_cm_ie_05_np = 7 - dd_cm_ie_05_ip,    ## Interest-Enjoy
         dd_cm_tp_02_np = 5 - dd_cm_tp_02_ip,    ## Theory-Praxis-Relation
         dd_cm_tp_04_np =     dd_cm_tp_04_ip,
         dd_cm_tp_06_np =     dd_cm_tp_06_ip, 
         dd_cm_ko_02_np = 5 - dd_cm_ko_02_ip,    ## Koherence
         dd_cm_ko_04_np = 5 - dd_cm_ko_04_ip, 
         
         ## BFLP text
         ed_bp_ie_05_np = 7 - ed_bp_ie_05_ip,    ## Interest-Enjoy
         ed_bp_tp_02_np = 5 - ed_bp_tp_02_ip,    ## Theory-Praxis-Relation
         ed_bp_tp_04_np =     ed_bp_tp_04_ip,
         ed_bp_tp_06_np =     ed_bp_tp_06_ip, 
         ed_bp_ko_02_np = 5 - ed_bp_ko_02_ip,    ## Koherence
         ed_bp_ko_04_np = 5 - ed_bp_ko_04_ip, 
         
         ## CLassroom size text
         ed_cs_ie_05_np = 7 - ed_cs_ie_05_ip,    ## Interest-Enjoy
         ed_cs_tp_02_np = 5 - ed_cs_tp_02_ip,    ## Theory-Praxis-Relation
         ed_cs_tp_04_np =     ed_cs_tp_04_ip,
         ed_cs_tp_06_np =     ed_cs_tp_06_ip, 
         ed_cs_ko_02_np = 5 - ed_cs_ko_02_ip,    ## Koherence
         ed_cs_ko_04_np = 5 - ed_cs_ko_04_ip,
         
         
        ## D-Index  FREE
         di_01_np = po_01_np - 0.5*(ab_01_np + re_01_np),
         di_02_np = po_02_np - 0.5*(ab_02_np + re_02_np),
         di_03_np = po_03_np - 0.5*(ab_03_np + re_03_np),
         di_04_np = po_04_np - 0.5*(ab_04_np + re_04_np),
         di_05_np = po_05_np - 0.5*(ab_05_np + re_05_np),
         di_06_np = po_06_np - 0.5*(ab_06_np + re_06_np),
         di_07_np = po_07_np - 0.5*(ab_07_np + re_07_np),
         di_08_np = po_08_np - 0.5*(ab_08_np + re_08_np),
         di_09_np = po_09_np - 0.5*(ab_09_np + re_09_np),
         di_10_np = po_10_np - 0.5*(ab_10_np + re_10_np),
         di_11_np = po_11_np - 0.5*(ab_11_np + re_11_np),
         di_12_np = po_12_np - 0.5*(ab_12_np + re_12_np),
         di_13_np = po_13_np - 0.5*(ab_13_np + re_13_np))


# Reject inverse coded original item
rawdata_np <- tbl_df(rawdata%>%
                       select(-ends_with("_ip"),
                              -starts_with("tx_"),
                              -starts_with("va_")
                              )
                     )




# Create dummy variables (sum constrasts) for source
rawdata_np$I_exp <- ifelse(rawdata_np$source == "exp", 1,
                                ifelse(rawdata_np$source == "erf", -1,0))


rawdata_np$I_wis <- ifelse(rawdata_np$source == "wis", 1,
                                ifelse(rawdata_np$source == "erf", -1,0))
         
```




## Reshape to long form & group mean centering
As MPlus requires the so called "long format" of multilevel data we reshaped our join to that format. Also we needed to group mean center the level-1 (within-person level) predictors, to make sure that the random intercept are interpretable as person specific means of the dependend variable.
```{r reshape to long, cache = T}

rawdata_long_np <- rawdata_np%>%
  mutate(source   = substr(Pseudonym, 1,3),
         rotation = substr(Pseudonym, 5,6))%>%
  gather(withinitem, value, starts_with("dd_") , starts_with("ed_"))%>%
  mutate(paradigm   = substr(withinitem, 1,2),
         topic      = substr(withinitem, 4,5),
         withinitem2 = as.factor(substr(withinitem, 7,14)))%>%
  select(-withinitem)%>%
  select(-starts_with("dd"))%>%
  select(-starts_with("ed"))%>%
  spread(withinitem2, value)%>%
  group_by(Pseudonym)%>%
  mutate(tr_01_pc = tr_01_np - mean(tr_01_np, na.rm = TRUE),   ## Group Mean Centering
         tr_02_pc = tr_02_np - mean(tr_02_np, na.rm = TRUE),
         tr_03_pc = tr_03_np - mean(tr_03_np, na.rm = TRUE),
         tr_04_pc = tr_04_np - mean(tr_04_np, na.rm = TRUE),
         ke_01_pc = ke_01_np - mean(ke_01_np, na.rm = TRUE),
         cl_01_pc = cl_01_np - mean(cl_01_np, na.rm = TRUE),
         cl_02_pc = cl_02_np - mean(cl_02_np, na.rm = TRUE),
         cl_03_pc = cl_03_np - mean(cl_03_np, na.rm = TRUE),
         ie_01_pc = ie_01_np - mean(ie_01_np, na.rm = TRUE),
         ie_02_pc = ie_02_np - mean(ie_02_np, na.rm = TRUE),
         ie_03_pc = ie_03_np - mean(ie_03_np, na.rm = TRUE),
         ie_04_pc = ie_04_np - mean(ie_04_np, na.rm = TRUE),
         ie_05_pc = ie_05_np - mean(ie_05_np, na.rm = TRUE),
         ko_01_pc = ko_01_np - mean(ko_01_np, na.rm = TRUE),
         ko_02_pc = ko_02_np - mean(ko_02_np, na.rm = TRUE),
         ko_03_pc = ko_03_np - mean(ko_03_np, na.rm = TRUE))%>%
  ungroup()


rawdata_long_np$IDnum <- as.numeric(as.factor(rawdata_long_np$Pseudonym))  ## Create numeric Person identifier for MPlus
rawdata_long_np$topic <- factor(rawdata_long_np$topic, levels=c("we", "cm", "bp", "cs"))  ## Reorder Factor Levels
rawdata_long_np$sourcenum <- as.numeric(as.factor(rawdata_long_np$source))  ## Convert Factor Levels to numeric factor for MPlus)
```



# Sample description
## Sample size
```{r}
rawdata$not_na <- rowMeans(is.na(rawdata)) # Variable which proportion NA/not NA 
plot(select(rawdata, -Pseudonym, -Welle, -rawid, -source, -zeit, -kurs)$not_na)     # Variable

# Total sample size
nrow(rawdata)

# Gender ratio
nrow(rawdata %>% filter(sex == 2))  # female
nrow(rawdata %>% filter(sex == 1))  # male
nrow(rawdata %>% filter(sex == 3))  # other

# Age
mean(rawdata$age, na.rm = T)
sd(rawdata$age, na.rm = T)

# semester
100/sum(!is.na(rawdata$sem))*sum(rawdata$sem <= 2, na.rm = T)                    # Percentage of semester 1 or 2
100/sum(!is.na(rawdata$sem))*sum(rawdata$sem <= 4 & rawdata$sem > 2, na.rm = T)  # Percentage of semester 3 or 4
```


## Gender



# Instruments
The questionaire contained between-person level variables (asked every student teacher once) as well as within-person level variables (asked each student teacher once per topic). The follwing code describes the (multi-level) confirmatory factor analyses (MCFA), which allowed us to also report estimations of reliability using McDonalds ω [@Dunn2013]. Therefore we first specified so called "independent clusters model of confirmatory factor analysis (ICM-CFA)". If the model fit was lower then our criteria, we estimated measurement error covariances (within on factor and choosen by modification indices) freely.  
Details about multi-level confirmatory factor analyses are given in the methods section of the corresponding article.

## Print functions
```{r printfunctions}
## Define a print function for MPlus-Output
fpf_mp <- function(x){  
  
  fm_tmp <- readModels(as.character(x))
  
  return(sprintf(
    "χ² = %s, _df_ = %s,
    CFI = %s, TLI = %s, 
    RMSEA = %s, SRMR~within~ = %s,
    SRMR~between~ = %s",
    round(fm_tmp$summaries$ChiSqM_Value,3), 
    fm_tmp$summaries$ChiSqM_DF,
    round(fm_tmp$summaries$CFI,3),
    round(fm_tmp$summaries$TLI,3),
    round(fm_tmp$summaries$RMSEA_Estimate,3),
    round(fm_tmp$summaries$SRMR.Within,3),
    round(fm_tmp$summaries$SRMR.Between,3)
  )
  )
}

## Define a reliability print function for within person variables
library(dplyr)
rpf_wv <- function(x){  
  
   reldat <- rawdata_long_np%>%
                    select(starts_with(as.character(x)), topic)%>%
                    select(-ends_with("pc"))%>%
                    group_by(topic)%>%
                    do(data.frame(alpha = MBESS::ci.reliability(data.frame(select(., starts_with(as.character(x)))))))
                      
  
  return(sprintf(
          "%s < ω < %s (union of 95%% CI [%s, %s])",
          round(min(reldat$alpha.est), 2),
          round(max(reldat$alpha.est), 2),
          round(min(reldat$alpha.ci.lower), 2),
          round(max(reldat$alpha.ci.upper), 2)
          )
  )
}

## Define a print function for lavaan-Output ##############################
fpf_la <- function(x){  

  fm_tmp <- fitmeasures(x)
                    
  return(sprintf(
          "χ² = %s, _df_ = %s, CFI = %s, TLI = %s, RMSEA = %s, SRMR = %s",
           round(fm_tmp[c("chisq")],3), 
                 fm_tmp[c("df")],
           round(fm_tmp[c("cfi")],3),
           round(fm_tmp[c("tli")],3),
           round(fm_tmp[c("rmsea")],3),
           round(fm_tmp[c("srmr")],3)
             )
       )
}


## Define a reliability print function for between person variables

rpf_bv <- function(x){  
  
   reldat <- rawdata_np%>%
                    select(starts_with(as.character(x)))%>%
                    select(-ends_with("pc"))
   relinfo <- MBESS::ci.reliability(data.frame(select(reldat, starts_with(as.character(x)))))
                      
  
  return(sprintf(
            "ω = %s, 95%% CI [%s, %s])",
            round(relinfo$est, 2),
            round(relinfo$ci.lower, 2),
            round(relinfo$ci.upper, 2)
            )
         )
}
```


## Perceived Theory-Practice-Integration
### MCFA
```{r MCFA_tp_unres, echo=T, warning=F, message=F, cache = F, eval = T, results = 'hide'}
rawdata_long_np$IDnum <- as.numeric(as.factor(rawdata_long_np$Pseudonym))

MCFA_tp_unres <- mplusObject(
  
   TITLE =  "MCFA__tp_unres",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np;
                CLUSTER = IDnum;",
  
   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
           
                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;",
   
   OUTPUT = "Standardized;",
   
   rdata = rawdata_long_np)

MCFA_tp_unres_fit <- mplusModeler(MCFA_tp_unres, "MCFA_tp_unres.dat", run = 1)
```

### Fit Indices of the MCFA:
`r fpf_mp("MCFA_tp_unres.out")`  

### Reliability estimates:
`r rpf_wv("tp")`


## Theory-Specific Relativism
```{r MCFA_tr_unres, echo=T, warning=F, message=F, cache = T, eval = T, results = 'hide'}
library(MplusAutomation)
MCFA_tr_unres <- mplusObject(
  
   TITLE =  "MCFA_tr_unres",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tr_01_np tr_02_np tr_03_np tr_04_np;
                     CLUSTER = IDnum;",
        
        
   MODEL    =      "%WITHIN%
                    trW BY tr_01_np tr_02_np tr_03_np tr_04_np;
        
                    %BETWEEN%
                    trB BY tr_01_np tr_02_np tr_03_np tr_04_np;
                           TR_03_NP WITH TR_01_NP;
                           TR_04_NP WITH TR_02_NP; ",  
   
   OUTPUT = "Standardized; MODINDICES",
   
   rdata = rawdata_long_np)

MCFA_tr_unres_fit <- mplusModeler(MCFA_tr_unres, "MCFA_tr_unres.dat", run = 1)
```

### Fit Indices of the MCFA:
`r fpf_mp("MCFA_tr_unres.out")`  

### Reliability estimates:
`r rpf_wv("tr")`

## Koherence with the topic
As a ICM-MCFA resulted in bad fit indices for the SRMR at the between level we fit a model, where the random intercepts only covaried.
```{r MCFA_ko_within, echo=T, warning=F, message=F, cache = T, eval = F, results = 'hide'}
library(MplusAutomation)
MCFA_ko_within <- mplusObject(
  
   TITLE =  "MCFA_ko_within",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = ko_01_np ko_02_np ko_03_np;
               
                     CLUSTER = IDnum;",
        
   MODEL    =      "%WITHIN%
                    koW BY ko_01_np(1)
                           ko_02_np(1)
                           ko_03_np(1);

                    %Between%
                    ko_01_np WITH ko_02_np ko_03_np;
                    ko_02_np WITH ko_03_np; ",   
   
   OUTPUT = "Standardized; Modindices",
   rdata = rawdata_long_np)

MCFA_ko_within_fit <- mplusModeler(MCFA_ko_within, "MCFA_ko_within.dat", run = 1)
```

### Fit Indices of the MCFA:
χ² = 9.162, _df_ = 1, CFI = 994, TLI = 962, RMSEA = .075, SRMR~within~ = .005, SRMR~between~ = .065

### Reliability estimates:
```{r, results="asis", warning = F, message = F}
  
   reldat_ko <- rawdata_long_np%>%
                    select(starts_with(as.character("ko_")), topic)%>%
                    select(-ends_with("pc"), -ko_04_np)%>%
                    group_by(topic)%>%
                    do(data.frame(alpha = MBESS::ci.reliability(data.frame(select(., starts_with(as.character("ko")))))))
                      
  
sprintf(
          "%s < ω < %s (union of .95CI[%s,%s])",
          round(min(reldat_ko$alpha.est), 2),
          round(max(reldat_ko$alpha.est), 2),
          round(min(reldat_ko$alpha.ci.lower), 2),
          round(max(reldat_ko$alpha.ci.upper), 2)
    
  )
```


## Knowledge about the topic
We assed knowledge about the topic with an single item.


## Epistemic development
```{r cfa_free, cache = T}
di.cfa.model <- "di =~ di_01_np + di_02_np + di_03_np + di_04_np + di_05_np + di_06_np + di_07_np + 
                       di_08_np + di_09_np + di_10_np + di_11_np + di_12_np + di_13_np
                       di_04_np ~~ di_05_np
                       di_03_np ~~ di_06_np"
di.cfa.fitted <- cfa(di.cfa.model, data = rawdata_np)
```

### Fit Indices of the CFA:
`r fpf_la(di.cfa.fitted)`  

### Reliability estimates:
`r rpf_bv("di_")`


## Epistemic beliefs inventory
```{r cfa_ebi, cache = T}

ebi.cfa.model <- "abs =~ stab_a_27 + stab_a_41 + rech_a_03 + rech_a_06 + rech_a_10 + komp_a_07 +
                         komp_a_20 + komp_a_42 + komp_a_39 + quel_a_08 + quel_a_11 + quel_a_35
                  rel =~ stab_r_04 + stab_r_18 + stab_r_23 + stab_r_21 + rech_r_17 + rech_r_33 +                           komp_r_22 + komp_r_30 + komp_r_43 + quel_r_09 + quel_r_34


                  stab =~ stab_a_27 + stab_a_41 + stab_r_04 + stab_r_18
                  rech =~ rech_a_03 + rech_a_06 + rech_a_10 + rech_r_17 + rech_r_33
                  komp =~ komp_a_07 + komp_a_20 + komp_a_42 + komp_a_39 + komp_r_22 + komp_r_30 + 
                          komp_r_43
                  quel =~ quel_a_08 + quel_a_11 + quel_a_35 + quel_r_09 + quel_r_34

                  quel_a_11 ~~ quel_a_35
                  stab_r_04 ~~ stab_r_23
                  rech_r_17 ~~ rech_r_33 " 



ebi.cfa.fitted <- cfa(ebi.cfa.model, data = rawdata)
```

### Fit Indices of the CFA:
`r fpf_la(ebi.cfa.fitted)`  

### Reliability estimates:
* Absolutism: ω = `r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_a_"))))$est, 2)`, 95% CI [`r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_a_"))))$ci.lower, 2)`, `r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_a_"))))$ci.upper, 2)`])
* Relativism: ω = `r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_r"))))$est, 2)`, 95 % CI[`r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_r_"))))$ci.lower, 2)`, `r round(MBESS::ci.reliability(data.frame(select(rawdata_np, contains("_r_"))))$ci.upper, 2)`])


## Connotative aspect of epistemic beliefs
```{r cfa_ceab, cache = T}
caeb.cfa.model <- " tex =~ te_01_np + te_02_np + te_03_np + te_04_np + te_05_np + te_06_np + 
                           te_07_np + te_08_np + te_09_np + te_10_np
                    var =~ vr_01_np + vr_02_np + vr_03_np + vr_04_np + vr_05_np + vr_06_np + 
                           vr_07_np
                           te_06_np ~~ te_10_np
                           te_05_np ~~ te_08_np
                           vr_02_np ~~ vr_04_np
                           te_03_np ~~ vr_03_np 
                           vr_04_np ~~ vr_07_np 
                           te_06_np ~~ te_07_np "


caeb.cfa.fitted <- cfa(caeb.cfa.model, data = rawdata_np)
```

### Fit Indices of the CFA:
`r fpf_la(caeb.cfa.fitted)`  

### Reliability estimates:
* Variability: `r rpf_bv("vr_")`
* Texture: `r rpf_bv("te_")`

## Muenster epistemic truthworthiness inventory
```{r cfa meti, cache = T}
meti.cfa.model <- "me =~ me_01_np + me_02_np + me_03_np + me_04_np + me_05_np + me_06_np
                   mi =~ mi_01_np + mi_02_np + mi_03_np + mi_04_np
                   mb =~ mb_01_np + mb_02_np + mb_03_np + mb_04_np

                   mi_01_np ~~ mi_02_np
                   mb_01_np ~~ mb_02_np
                   mi_03_np ~~ mi_04_np
                   mb_03_np ~~ mb_04_np"

meti.cfa.fitted <- cfa(meti.cfa.model, data = rawdata_np)
```

### Fit Indices of the CFA:
`r fpf_la(meti.cfa.fitted)`  

### Reliability estimates:
* Expertise: `r rpf_bv("me_")`
* Integrity: `r rpf_bv("mi_")`
* Benevolence: `r rpf_bv("mb_")`



# Results
This sections provides the code and output of the analyses we conducted to investigate our hypotheses. Note that the heading the same than in the corresponding article.

## Predictive Effects of Source (H1)

### M3: Multi-Group MCFA Model
```{r MGMCFA_strong_invariance, cache = T, eval = T, results = 'hide', warning = F, message = F}

### MGMCFA Modell _____________________________________________________________________

MGMCFA_tp_strong <- mplusObject(
  
   TITLE =  "MGMCFA_tp_strong",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np;
                GROUPING IS sourcenum (1 = erf 2 = exp 3 = wis);
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
   
                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
   
                 tp_06_np@0   ;",

   OUTPUT = "Standardized MODINDICES(5);",
   rdata = rawdata_long_np)

MGMCFA_tp_strong_fit <- mplusModeler(MGMCFA_tp_strong, "MGMCFA_tp_strong.dat", run = 1)
```

* The fitindices of M3 were: `r fpf_mp("MGMCFA_tp_strong.out")`


### M4: MIMIC Model with source indicator variables as predictors
```{r MIMIC_pred_source, cache = T, eval=T, warning = F, message = F, results = 'hide'}

# Dummyvariables for MIMIC Model 
rawdata_long_np$I_exp <- ifelse(rawdata_long_np$source == "exp", 1, 0)
rawdata_long_np$I_wis <- ifelse(rawdata_long_np$source == "wis", 1, 0)


### MIMIC_pred_source Modell  _____________________________________________________________________

MIMIC_pred_source <- mplusObject(
  
   TITLE =  "MIMIC_pred_source",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np I_exp I_wis;

                BETWEEN = I_exp I_wis;
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;

                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 tp_06_np@0;
                 TPB ON I_exp I_wis;",
   
   OUTPUT = "Standardized MODINDICES(5);",
   
   rdata = rawdata_long_np)

MIMIC_pred_source_fit <- mplusModeler(MIMIC_pred_source, "MIMIC_pred_source.dat", run = 1)
```

* The fitindices of M4 were: `r fpf_mp("MIMIC_pred_source.out")`


## Predictive Effects of epistemic beliefs (H2)

### M5: Predictive Effects of D-Index
```{r MGMLSEM_pred_di_man, cache = T, eval=T, results = 'hide', warning = F, message = F}

rawdata_long_np <-
  rawdata_long_np%>%
    mutate(di_gc = scale(rowMeans(data.frame(di_01_np, di_02_np, di_03_np, di_04_np, di_05_np, 
                                     di_06_np, di_07_np, di_08_np, di_09_np, di_10_np,
                                     di_11_np, di_12_np, di_13_np), na.rm = T), scale = F),
           tr_pc = rowMeans(data.frame(tr_01_pc, tr_02_pc, tr_03_pc, tr_04_pc), na.rm = T),
           di_gc = ifelse(scale(di_gc) > 3.29, NA, ifelse(scale(di_gc) < -3.29, NA, di_gc)),  ## removing outliers
           tr_pc = ifelse(scale(tr_pc) > 3.29, NA, ifelse(scale(tr_pc) < -3.29, NA, tr_pc)),  ## in the way we preregistered
           di_gc_exp = di_gc*I_exp,
           di_gc_wis = di_gc*I_wis)


### MGMCFA Modell  _____________________________________________________________________

MIMIC_pred_di_man <- mplusObject(
  
   TITLE =  "MIMIC_pred_di_man",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np
                tr_pc
                di_gc di_gc_exp di_gc_wis I_exp I_wis;

                WITHIN = tr_pc;
                BETWEEN = di_gc di_gc_exp di_gc_wis I_exp I_wis;
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 TPW ON tr_pc;

                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 tp_05_np@0;
                 TPB ON di_gc di_gc_exp di_gc_wis I_exp I_wis;",
   
   OUTPUT = "Standardized MODINDICES(5);",
   
   rdata = rawdata_long_np)

MIMIC_pred_di_man_fit <- mplusModeler(MIMIC_pred_di_man, "MIMIC_pred_di_man.dat", run = 1)
```

* The fitindices of M5 were: `r fpf_mp("MIMIC_pred_di_man.out")`
* The standardized predictive effects of M5 were:
```{r results="asis", cache = F}
MIMIC_pred_di_man_results <- readModels("MIMIC_pred_di_man.out")
pander::pander(MIMIC_pred_di_man_results$parameters$stdyx.standardized%>% filter(grepl("ON", paramHeader)))
```



### M6: Predictive Effects of EBI
```{r MIMIC_pred_ebi_man, cache = T, eval=T, results = 'hide', warning = F, message = F}

rawdata_long_np <-
  rawdata_long_np%>%
    mutate(abs_gc = scale(rowMeans(data.frame(stab_a_27, stab_a_41, rech_a_03, rech_a_06, rech_a_10, komp_a_07,
                                     komp_a_20, komp_a_42, komp_a_39, quel_a_08, quel_a_11, quel_a_35), na.rm = T),
                          scale = F),
           rel_gc = scale(rowMeans(data.frame(stab_r_04, stab_r_18, stab_r_23, stab_r_21, rech_r_17, rech_r_33,  
                                     komp_r_22, komp_r_30, komp_r_43, quel_r_09, quel_r_34), na.rm = T), 
                          scale = F),
           abs_gc = ifelse(scale(abs_gc) > 3.29, NA, ifelse(scale(abs_gc) < -3.29, NA, abs_gc)), ## removing outliers
           rel_gc = ifelse(scale(rel_gc) > 3.29, NA, ifelse(scale(rel_gc) < -3.29, NA, rel_gc)), ## in the way we preregistered
           abs_gc_exp = abs_gc*I_exp,
           rel_gc_exp = rel_gc*I_exp,
           abs_gc_wis = abs_gc*I_wis,
           rel_gc_wis = rel_gc*I_wis)

### MIMIC_pred_ebi_man Modell  _____________________________________________________________________

MIMIC_pred_ebi_man <- mplusObject(
  
   TITLE =  "MIMIC_pred_ebi_man",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np
                tr_pc
                abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis 
                I_exp I_wis;

                WITHIN =  tr_pc;
                BETWEEN = abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis
                          I_exp I_wis;
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 TPW ON tr_pc;

                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 tp_05_np@0;
                 TPB ON abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis 
                        I_exp I_wis;
   
   
   ",
   OUTPUT = "Standardized MODINDICES(5);",
   rdata = rawdata_long_np)

MIMIC_pred_ebi_man_fit <- mplusModeler(MIMIC_pred_ebi_man, "MIMIC_pred_ebi_man.dat", run = 1)
```

* The fitindices of M6 were: `r fpf_mp("MIMIC_pred_ebi_man.out")`
* The standardized predictive effects of M6 were:
```{r results="asis", cache = F}
MIMIC_pred_ebi_man_results <- readModels("MIMIC_pred_ebi_man.out")
pander::pander(MIMIC_pred_ebi_man_results$parameters$stdyx.standardized%>% filter(grepl("ON", paramHeader)))
```





## Confounders of Predictive Effects of epistemic beliefs

### M7: Confounders of Predictive Effects D-Index (H3)

```{r MIMIC_conf_di_man, cache = T, eval = T, results = 'hide', warning = F, message = F}

### Generate arithemtic means of scales  _____________________________________________________________________
rawdata_long_np <- rawdata_long_np%>%
  mutate(cl_pc = rowMeans(data.frame(cl_01_pc, cl_02_pc, cl_03_pc), na.rm = T),
         ko_pc = rowMeans(data.frame(ko_01_pc, ko_02_pc, ko_03_pc), na.rm = T),
         me_np = rowMeans(data.frame(me_01_np, me_02_np, me_03_np, me_04_np, me_05_np, me_06_np), na.rm = T),
         mi_np = rowMeans(data.frame(mi_01_np, mi_02_np, mi_03_np, mi_04_np), na.rm = T),
         mb_np = rowMeans(data.frame(mb_01_np, mb_02_np, mb_03_np, mb_04_np), na.rm = T),
         ko_pc = ifelse(scale(ko_pc) > 3.29, NA,ifelse(scale(ko_pc) < -3.29, NA, ko_pc)),
         me_np = ifelse(scale(me_np) > 3.29, NA,ifelse(scale(me_np) < -3.29, NA, me_np)),
         mi_np = ifelse(scale(mi_np) > 3.29, NA,ifelse(scale(mi_np) < -3.29, NA, mi_np)),
         mb_np = ifelse(scale(mb_np) > 3.29, NA,ifelse(scale(mb_np) < -3.29, NA, mb_np)))



### MIMIC_conf_di_man Modell  _____________________________________________________________________

MIMIC_conf_di_man <- mplusObject(
  
   TITLE =  "MIMIC_conf_di_man",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np
                tr_pc ke_01_pc ko_pc 
                di_gc di_gc_exp di_gc_wis I_exp I_wis me_np mi_np mb_np;

                WITHIN =  tr_pc ke_01_pc ko_pc;
                BETWEEN = di_gc di_gc_exp di_gc_wis I_exp I_wis me_np mi_np mb_np;
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;

                 TPW ON tr_pc ke_01_pc ko_pc ;

                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 tp_05_np@0;
                 TPB ON di_gc di_gc_exp di_gc_wis I_exp I_wis me_np mi_np mb_np; ",
   
   OUTPUT = "Standardized MODINDICES(5);",
   
   rdata = rawdata_long_np)

MIMIC_conf_di_man_fit <- mplusModeler(MIMIC_conf_di_man, "MIMIC_conf_di_man.dat", run = 1)
```

* The fitindices of M7 were: `r fpf_mp("MIMIC_conf_di_man.out")`
* The standardized predictive effects of M7 were:
```{r results="asis", cache = F}
MIMIC_conf_di_man_results <- readModels("MIMIC_conf_di_man.out")
pander::pander(MIMIC_conf_di_man_results$parameters$stdyx.standardized%>% filter(grepl("ON", paramHeader)))
```


### M8: Confounders of Predictive Effects EBI (H3)

```{r MGPATH_conf_eb_ebi, cache = T, eval = T, results = 'hide', warning = F, message = F}

### MIMIC_conf_ebi_man Modell  _____________________________________________________________________

MIMIC_conf_ebi_man <- mplusObject(
  
   TITLE =  "MIMIC_conf_ebi_man",
   
   ANALYSIS =  "TYPE = TWOLEVEL;",
    
   VARIABLE =  "USEVARIABLES = tp_01_np tp_02_np tp_03_np tp_04_np 
                tp_05_np tp_06_np
                tr_pc ke_01_pc ko_pc 
                abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis
                I_exp I_wis me_np mi_np mb_np;

                WITHIN =  tr_pc ke_01_pc ko_pc;
                BETWEEN = abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis
                          I_exp I_wis me_np mi_np mb_np;
                CLUSTER = IDnum;",
   

   MODEL =      "%WITHIN%
                 TPW BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;

                 TPW ON tr_pc ke_01_pc  ko_pc ;

                 %BETWEEN%
                 TPB BY tp_01_np tp_02_np tp_03_np tp_04_np tp_05_np tp_06_np;
                 tp_05_np@0;
                 TPB ON abs_gc rel_gc abs_gc_exp rel_gc_exp abs_gc_wis rel_gc_wis
                        I_exp I_wis me_np mi_np mb_np;",
   
   OUTPUT = "Standardized MODINDICES(5);",
   
   rdata = rawdata_long_np)

MIMIC_conf_ebi_man_fit <- mplusModeler(MIMIC_conf_ebi_man, "MIMIC_conf_ebi_man.dat", run = 1)
```

* The fitindices of M8 were: `r fpf_mp("MIMIC_conf_ebi_man.out")`
* The standardized predictive effects of M8 were:
```{r results="asis", cache = F}
MIMIC_conf_ebi_man_results <- readModels("MIMIC_conf_ebi_man.out")
pander::pander(MIMIC_conf_ebi_man_results$parameters$stdyx.standardized%>% filter(grepl("ON", paramHeader)))
```


# Literature